This two-story, oval rotunda acts as a central hub for the prison, as well as its primary entrance. It is filled with a great number of chairs all set facing inwards like an auditorium. They are centered around a square enclosure with an iron grill: a guard shack for processing visitations. In that case, this prison was clearly built for a more routine breed of prisoner.\\

Many chairs have been ripped out of the floor and piled up against the main entrance, along with tables and furniture pilfered from elsewhere in the building. It must have taken quite some effort to construct such an extensive barricade; it’s ten paces deep and nearly reaches the second story. Whatever it was meant to keep out doesn’t appear to have penetrated the complex--at least, not this way.\\

Two sets of stairs curve along the rotunda’s circumference; one leads up, the other down. Their landings meet before a doorway, which is centered in the wall opposite the main entrance. One of the doors has been ripped out, revealing an open office on the other side. A second glance at the barricade reveals that the missing door was likely the first object thrust against the main entrance.\\

The long ends of the rotunda's oval present two security hallways, which lead to the complex’s twin cell blocks. One such hallway is streaked with scorchmarks. The other leads back to the block where you first awakened.\\

Those Everloyal comrades you’ve rescued have gathered here. It’s a safe spot to take a rest, and anything you leave here won’t go missing--hopefully.\\

> Take a \emph{short reprieve}\\
> Access your stash\\
> Examine the barricaded prison entrance -- \turnto{c32}\\
> Speak with the rescued Everloyal -- \turnto{c36}\\
> Enter the security hallway -- \turnto{c218}\\
> Enter the scorched security hallway -- \turnto{c35}\\
> Enter the back offices -- \turnto{c312}\\
> Take the stairs up -- \turnto{c34}\\
> Take the stairs down -- \turnto{c33}