And it’s occupied.\\

“No! No... O-friend?”\\

You barrel into the lavatory, nearly knocking your ratfriend into the honeyhole, and then slam the door behind you. It soon begins to rattle and shake, but you lean all your weight onto its latch to keep it closed. Try as they might, those adventurers cannot pull it open.\\

A vicious knocking soon begins--but this door has surely sustained a similar such pounding many times before. Eventually, the knocker quits. You can hear low, angry whispers from the barracks outside. Then the sounds of struggle and huffing. And finally nothing.\\

Time passes. You and your ratfriend wait with clenched noses and straining ears. Eventually Niki places its face against the cracks in the door and takes a look around.\\

“Gone-gone.”\\

The two of you spill from the lavatory, gasping for clean air. The adventurers are gone, and were diligent in leaving none of their gear behind. The grappling hook affixed to a window implies that they won't be returning.\\

\emph{If Lustrous Nastya was defeated:}\\
>> Soul of a Greedy Sorceress (10)\\

\emph{If Goldhand Vitalik was defeated:}\\
>> Soul of a Sneaky Mercenary (10)\\

\emph{If Goldhand Sergey was defeated:}\\
>> Soul of a Fickle Mercenary (10)\\

Ratfriend Niki approaches you in sheepish strides, its head dipped low as if expecting some rebuke.\\
\notegain{c311a} Ratfriend Niki is rescued\\

"Ro-tunda? Okay-kay."\\

Niki scampers through the wreck and ruin of the guard barracks and disappears into the complex.\\

>> Explore the barracks -- \turnto{c327}