Beset by the panic of your flight, you find yourself seeking high places. The minaret stairwell draws you like a lodestone. You race up its steps, leaving the weird cries of your pursuer below.\\

Vast sections of the level overhead are gone. The remaining swathe is perched perilously on a ribcage of support columns. A peninsula of flagstone tiles extends to the summit of the lone, surviving stairwell.\\

This stairwell stands teetering on the mezzanine's jagged precipice. Sections of its circular wall have dropped away, revealing glimpses of the winding staircase within. Gazing up the length of it, you reckon it's about as safe as anything else in this forsaken place. Another glance downwards reveals the mad red glow of that thing still searching for you throughout the mezzanine.\\

"And who are ye to strive to such great heights?"\\

A man watches you from the remnants of the upper floor. He is dressed in a prisoner's rags, but stands with a posture that implies that his station in life was great once.\\

"I know ye. And ye could once say the like, but I reckon by the dark in yer eyes that ye know me no longer. Like a leveret ye are; and ye come seeking salvation, but our kind does not proffer it to paupers."\\

"We'll test the steel beneath yer rust. Like as not we'll have much need of it--though ye seem to trust it very little."\\

"Come and see. Come and see."\\

And with that, the man turns and disappears into the wreckage overhead.\\

At the summit of the stairwell, you find its archway is filled with a sheet of fog.\\

>> Broach the fog barrier -- \turnto{c317}\\