Stepping through the melted bars, you discover that the prisoners had pulled their cell’s bunkbeds together into a makeshift palisade. It did them little good, for the wooden frames have been burnt to cinders. Not a single body in sight, either. They must all be in the nest.\\

You pace slowly through the cell. The shadows of its burnt wreckage stretch along the walls in strange and unnerving shapes. Spindly, jagged lines that criss and cross through the threatening quiet.\\

Then something shuffles against the floor and quickly stops. It came from the far corner: beneath an unsinged bunk.\\

As you draw closer, the air builds with an electric tension. And when you bend down to take a look beneath the rack, a shrill scream sends you reeling into the supline.\\

“O, you’re not hollow!”\\

A dimunitive, young girl crawls out from beneath the bed--like some farcical imitation of a child’s bogeyman. And, braced on her hands and knees, she dips her head in apology.\\

“I’m \lisp orry! I didn’t mean to \lisp care you!”\\

The girl talks with her hands: gesticulating rapidly while she lisps out an explanation.\\

“I heard the noi\lisp e\lispx of combat but... well, I didn’t think anyone would come for me--anyone \lisp till \lisp ane that i\lisp . I’m a\lisp uming... you killed him, then?”\\

The girl reclines onto her knees.\\
“Ah, he wa\lispx the fir\lisp t to lo\lisp e hi\lispx mind to the curse. Then he began to... \emph{change.}”\\

"We threw him out into the fog. But, a\lispx I'm \lisp ure you can \lisp ee..."\\

The girl sweeps her hand about the wreckage.\\
"He came back."\\

“I’m A\lisp trid, by the way. But my friend\lispx call me Littletongue. And I think you’ve more than qualified a\lispx a friend.”\\

>> Explain the situation -- \turnto{c325x1}