You look over the floor plan awhile, trying to tie its geometric shapes to the areas you’ve encountered.\\

You are presently in the rotunda, which functions as a main entrance, central hub, and visitation room. It also plays facade to a larger building that hosts the staff facilities. The offices, mess hall, and a kitchen lay on the building’s first floor; and the guard barracks is on the second floor, along with the warden’s private quarters.\\

As Littletongue stated earlier, there appears to be an underground dock for receiving prisoners and shipments. It lays directly beneath you, pointed southeast: askant from the prison’s easterly facing direction.\\

Two security hallways join the rotunda to the complex’s twin cell blocks. A pair of armories on the second floor also have reinforced doors leading to their respective blocks. The blocks themselves consist of a common area surrounded by large cells, which is overlooked by a mezzanine level. This mezzanine contains additional cells, as well as a hygiene processing room. A catwalk is positioned above each cell block, presumably to be patrolled by guards looking down into the common area. And finally, a third floor serves as solitary confinement.\\

Something sticks out to you: a smudge mark next to the warden’s quarters is obscuring a small room. It might just be a lavatory, but the smudge seems purposeful in nature. Someone disagreed with this room making it into the floor plan.\\
\notegain{c36b} There is a hidden room in the warden’s quarters\\

>>  Return to the Everloyal -- \turnto{c36}