You wander through the halls of the complex’s second floor. The floor's layout appears to be typical for an administrative building: a circuit hallway begirt on both sides by concentric series of rooms. One end passes by the rotunda, and the other borders what appears to be a barracks--its entrance is shrouded by fog.\\

This section has seen mortal combat. Dead guards litter the floor, their faces transfixed in various masks of anger and fear. Cold hands are left gripping an assortment of armaments--they managed to make it to an armory at some point during the assault, though it did them little good.\\
\gain{Spear}\\
\gain{Kite Shield}\\
\gain{Shortsword}\\

Despite being armed and armored, many of the dead guards are still in their smallclothes. A band of half-naked men wearing metal cuirasses over their long johns. It lends a grim, comical element to the scene.\\

One of these corpses is not like the others: a giant of a man dressed in strange, colorful leathers. He lays in the supline, propped up by no less than four spears. Both of his lifeless hands are still welded to the hilt of a battleaxe. The dead guards and arcs of blood streaking the walls must have been his doing. The only clue as to this man's identity is the broach of a golden hand pinned to his collar.\\
>> Soul of a Goldhand Warrior (10)\\
\gainx{Battleaxe}\\

A heavy door reinforced with iron crossbars seems to guard something important--probably an armory. But it's dented from the other side to such an extent that it's locks are inoperable. You won't be opening it from here.\\

> Continue to the other side of the hallway -- \turnto{c37}\\
> Explore this hallway's rooms -- \turnto{c38x1}\\
\requiresx{8+ ATT} Examine the giant's corpse further -- \turnto{c38x2}\\
\requiresx{c310a} Enter the destroyed armory -- \turnto{c310}\\
\requiresx{NOT c311a} Broach the fog barrier -- \turnto{c311}\\
\requiresx{c311a} Return to the guards' barracks -- \turnto{c327}\\
> Return to the rotunda -- \turnto{c34}