\section{Character Creation}
\hbadness=99999
\label{chargen}
\hypertarget{chargen}{}
It is dark. A barred window casts a series of dim slivers onto the flagstone floor. The shadows of tiny, crawling things make their way along the illuminated mortar. You do not know where you are, or how you came to be here.\\
\emph{>> Iterate through the steps of the character creation process, altering the character sheet as instructed.\\
>> Begin by marking a score of 7 for each Primary Statistic on the character sheet.}

\subsection*{Grasp at Your Fading Memories}
They slip through your conscious thoughts, leaving only the slight stain of their passing: those disconnected fragments that soon fade again like embers into a night sky. When you strain in recollection, what do you envision?\\
\emph{>> Select one option:}

\begin{multicols*}{2}
\subsubsection*{A Labyrinth of Streets}
Bare feet on cobblestone. People, but not faces. Smell of human refuse. Music and colored streamers. Cacophony of voices. Hunger.\\
\emph{>> DEX + 1; ATT + 1; VIT - 1 }

\subsubsection*{An Endless Weald}
Rain on a thatched roof. Wolves howling. Smell of split wood. Taste of mushrooms. Owl’s watchful eyes. Long walks with heavy loads. Fear.\\
\emph{>> END + 1; VIT + 1; ATT - 1 }

\subsubsection*{A Garden Terrace}
Saying the words; performing the motions. Haltering practice of chords. Stiff and sweltering costume. Taste of wine. Boredom.\\
\emph{>> INT + 1; DEX + 1; END - 1 }

\subsubsection*{An Idyllic Countryside}
Smell of pie: meat and greens. Goose honks; dog barks. Festival lanterns. Crunch of the trail. Cool water against the skin. Endless cavalcade of clouds.\\
\emph{>> VIT + 1; FTH + 1; INT - 1 }

\vspace*{\fill}
\columnbreak

\subsubsection*{A Vast Horizon}
Gulls squawking. Smell of fish. Pinch of sunburn. Clear days; storms. Sand underfoot. Aching palms. Rush of wind against the face.\\
\emph{>> FTH + 1; STR + 1; DEX - 1}

\subsubsection*{A Dour Swampland}
Smell of decay. Feet sloshing in soaked boots. Slight chill. Taste of eel and crayfish. Clinking of a pole lantern. Crackling fire. Haunting, distant calls.\\
\emph{>> ATT + 1; INT + 1; STR - 1 }

\subsubsection*{A Frigid Highland}
Bleating sheep. Creaking troika. Taste of mutton. Crunch of snow. Timeless vistas. Distant horns. Shivering cold.\\
\emph{>> STR + 1; END + 1; FTH - 1 }
\end{multicols*}

\subsection*{Examine Your Hands}
You hold your hands up to the faint light. There was skill in them once; you can almost feel them at work, even now. It’s as if they retain a memory all of their own. As they grasp and ungrasp, what do you recall?\\
\emph{>> Select one option:}

\begin{multicols*}{2}
\subsubsection*{A Well-Worn Pickaxe}
Pain. Time to work the left hand; give the right a little rest. No--still hurts there, too.\\
\emph{>> VIT + 2; END + 1; DEX - 1}

\subsubsection*{A Clenched Fist}
You punch it into your other hand, and wipe at your nose. Time to earn some coin.\\
\emph{>> END + 2; STR + 1; INT - 1}

\subsubsection*{A Wrapped \& Tarred Hilt}
The hilt jostles in your grip. One, two; one, two. Then suddenly, it isn’t a game anymore. The hilt shakes, despite your grip being tighter than ever before.\\
\emph{>> STR + 2; FTH + 1; ATT - 1}

\subsubsection*{A Lacquered Bow}
The string presses into your cheek. In your mind’s eye, you can see the arrow’s flight before it ever leaves your fingers.\\
\emph{>> DEX + 2; VIT + 1; STR - 1}

\subsubsection*{Playing Cards}
You lift the corners. Bad hand. Across the table, a mouth twitches. Bad hand. You shake your wrist a little. Good hand.\\
\emph{>> ATT + 2; DEX + 1; END - 1}

\subsubsection*{A Silver Goblet}
One hand pinches the stem, the other gesticulates. Emphasizing your words, circling the clever phrases. You are making your point quite clear.\\
\emph{>> INT + 2; ATT + 1; FTH - 1}

\subsubsection*{Sheep Entrails}
Lay them out. Poke them into place. Read carefully through the gore. There: an ill omen.\\
\emph{>> FTH + 2; INT + 1; VIT - 1}

\vfill
\columnbreak

\subsubsection*{A Wooden Yoke}
You pull. Stubborn bastard. You pull again. Damn it.\\
\emph{>> VIT + 2; STR + 1; ATT - 1}

\subsubsection*{Leather Reigns}
Another long ride--and hopefully, an uneventful one.\\
\emph{>> END + 2; VIT + 1; DEX - 1}

\subsubsection*{A Heavy Tool}
Clank of hammer; snore of saw. Smell of sawdust; heat of the forge. You squint to see your work clearer, and wipe the sweat from your brow.\\
\emph{>> STR + 2; DEX + 1; INT - 1}

\subsubsection*{A Hemp Rope}
Don’t look down. Almost there. You grab hold of the windowsill and pull yourself up. Once inside the darkened room, you carefully lower your sack to the floor.\\
\emph{>> DEX + 2; END + 1; VIT - 1}

\subsubsection*{A Marionette Paddle}
The manikin spins and dances. His face is all-too-familiar. The children might not catch the meaning now, but it will seep into their minds like a poison.\\
\emph{>> ATT + 2; INT + 1; FTH - 1}

\subsubsection*{An Owl Quill}
Your knuckles ache. You flex and unflex your hand, and grasp the quill again. Straining against the dim light, you carefully illustrate another vine entwined about the letter L.\\
\emph{>> INT + 2; FTH + 1; END - 1}

\subsubsection*{A Brass Chime}
Ring it once. Ring it again. Call them to you: the faithful, the curious, and especially the hecklers. They, most of all, must bear witness.\\
\emph{>> FTH + 2; ATT + 1; STR - 1}

\vfill
\end{multicols*}
\pagebreak

\subsection*{Collect Your Keepsake}
From above, there comes the pitter patter of droplets. A few pass through the barred window, and splash upon your cheeks. When the smell of petrichor strikes your senses, it stirs your failing memory to life.\\
Now you are pulling up the loose stone again--you are fishing out your treasure from the grit--you are cradling it in your weathered hands. This thing you hide so dearly: what is it?\\
\emph{>> Select one option:}

\begin{multicols}{2}
\subsubsection*{A Coin}
You pinch it by the rim, letting the light catch on its dull face. This coin is worth far more to you than its mere valuation.\\
\emph{>> STR + 1}

\subsubsection*{A Figurine}
You brush the dirt from the little figure’s face, like a tender parent might. It is so very important to keep it from weathering.\\
\emph{>> VIT + 1}

\subsubsection*{A Ring}
You slip it over your bony finger, then take it off again. It fits all the better as you grow more emaciated.\\
\emph{>> DEX + 1}

\subsubsection*{A Locket}
You pry it open, careful not to let any dirt fall inside, and risk a glance at the familiar likeness within.\\
\emph{>> END + 1}

\vspace*{\fill}
\columnbreak

\subsubsection*{A Fingerbone}
You lay it widthwise across your own bony fingers. The power that emanates from it is as strong as ever.\\
\emph{>> FTH + 1}

\subsubsection*{A Letter}
You clutch the decaying pages to your chest. Each reading of them feels fresh anew, thanks to your dwindling mind.\\
\emph{>> INT + 1}

\subsubsection*{A Fetish}
You hold it at length, as if it might bite you. A grotesque depiction, to be sure, but one you’re quite fond of.\\
\emph{>> ATT + 1}

\subsubsection*{A Pendant}
You hold the pendant up to the dim light. It’s quite possibly worthless--possibly.\\
\notegain{!!x11a!!} Possesses the pendant
\begin{tcolorbox}
\textbf{Note:} When a note is bracketed by !!, it is a permanent note, and is not erased during \textbf{End Chapter} actions.
\end{tcolorbox}
\end{multicols}
\hrule
\ \\
\ \\
Whatever meaning this keepsake holds, only you can say. But whether that memory is merely the product of a fragmented mind, not even its keeper could ever truly be certain.\\
\emph{>> Fill-in the first \refto{MEM} slot on the character sheet for your personal memento\\
>> Mark the first \refto{HMN} box}
\begin{tcolorbox}
\textbf{Note:} In \emph{Everloyal}, the character’s maximum \refto{HMN} is determined by their number of \reftoit{mementos}. Each acquired \reftoit{memento} fills-in a \refto{MEM} slot, which enables its accompanying \refto{HMN} slot to hold Humanity.\\
When the character gains or loses Humanity, an available \refto{HMN} box is marked or erased.\\
A \refto{MEM} slot is only erased if the character loses or destroys the accompanying \reftoit{memento}.
\end{tcolorbox}

\subsection*{Ruminate on the Pain}
As you cradle your treasure, the damp air reignites a nostalgic sting; a hurting from somewhere deep in the remote histories of your past. From whence it came, you do not know, but it dutifully reminds you of its presence time and again. This old pain that’s surfaced now: what wounds you?\\
\emph{>> Select one option:}

\begin{multicols}{2}
\subsubsection*{Chronic Fever}
You turn your face up to the rain, and wipe its droplets across your brow. It helps cool the fever--but not by much.\\
\emph{>> VIT - 1; Any Primary Stat + 1}

\subsubsection*{Wracked Lungs}
You cough and convulse, but to no avail. For a moment, it feels as though you might drown on dry land.\\
\emph{>> END - 1; Any Primary Stat + 1}

\subsubsection*{Wasting Illness}
You drag an arm across the stone floor, and lay it in your lap. It’s fallen asleep again, and soon feels as though you’d plunged it into a nest of hornets.\\
\emph{>> STR - 1; Any Primary Stat + 1}

\subsubsection*{A Missing Eye}
You poke a finger into the hole that once held your eye. Wherever did it go?\\
\emph{>> DEX - 1; Any Primary Stat + 1}

\vspace*{\fill}
\columnbreak

\subsubsection*{A Maimed Hand}
You are missing a number of fingers from one hand. Funny how it feels as if they’re still there.\\
\emph{>> ATT - 1; Any Primary Stat + 1}

\subsubsection*{Splitting Headaches}
They’ve started again. You bury your eyes in your palms and wait for them to pass.\\
\emph{>> INT - 1; Any Primary Stat + 1}

\subsubsection*{Mutilated Genitalia}
O, right--\emph{that}.\\
\emph{>> FTH - 1; Any Primary Stat + 1}

\subsubsection*{Scars}
They criss cross your body like the lattices of a fisherman’s net. All from one source, or the accumulation of years?\\
\emph{>> No changes}\\
\end{multicols}
\hrule
\ \\
\ \\
Then suddenly the light is gone, taking all earthly sense with it. You feel yourself slipping: down to starless skies of madness. How many times have you repeated this labor? Finding and losing; forgetting and remembering and then forgetting again. No! You reach for something--anything to latch onto.

\vfill

\subsection*{Try to Remember Your Name}
What was it? It should be so simple, and yet...\\

As a necessity of your vocation, you have had many. They march across your tongue to a familiar cadence, but you cannot discern the original from its phalanx of impostors. Out of desperation, you whisper one to yourself. What is it?\\
\emph{>> Write a name on the character sheet}\\

\pagebreak

\subsection*{Affirm Your Purpose}
You once again teeter on the precipice of nothingness: rocking back and forth, clutching your keepsake to your heart, and repeating that glib moniker to yourself like a mantra. It is a futile effort. You will forget as you have innumerable times before. And perhaps you will remember yourself again, or maybe you conjure up a new identity with each bout of clarity--like some ironic punishment for your life’s work: that web of lies and misdeeds...\\
\ \\
For there is one facet of yourself which you could never forget. Etched into your skin: your very purpose within this mortal coil. You trace the Sign with a finger. It is your light and your anchor; the flotsam you cling to in this capsized world...\\
\emph{>> Mark \textbf{SL} as 5\\
>> Calculate all Distributory Values\\
>> Finalize the status sheet}

\begin{center}
\vspace*{\fill}
{\Large
Once-Risen and Twice-Slain\\
The Black and Golden Key\\
King of all Secrets\\
\textbf{Av*rn-Z*l}\\
\ \\
His Faithful Gather in Furtive Circles\\
They Know Their kin by His Sign\\
And the Promise That was Made:\\
He Walked This World Once, and Shall Walk Again...\\
\ \\
\ \\
{\Huge \textbf{E V E R L O Y A L }}
}
\vspace*{\fill}
\end{center}

\hyperlink{scenres}{\textbf{Turn to: Scenario Resolution (Page \pageref{scenres}})}