\subsection{Guts}
Guts are fighting techniques and stances that can give a warrior a much-needed edge in combat.
\begin{itemize}
\item \textbf{Catalyst:} None
\item \textbf{Bonus:} None
\item \textbf{Notes:} “Stances” are Free reactions committed at the beginning of the \emph{counterbeat}, which take effect for that entire \emph{counterbeat}. They do not prevent the character from committing a reaction during the first enemy attack. Only one Stance may be activated per \emph{counterbeat}
\end{itemize}

\begin{center}
\begin{tabularx}{\textwidth}{p{0.1\textwidth}p{0.1\textwidth}p{0.05\textwidth}p{0.05\textwidth}p{0.1\textwidth}p{0.46\textwidth}}
\hline
\rowcolor{white} \textbf{Name} & \textbf{Req} & \textbf{Int} & \textbf{FP} & \textbf{SP} & \textbf{Effects}\setcounter{rownum}{0}\\
\hline
\makeitem{Adrenaline Surge} & END: 10 & 2 & 4 & F & Take 1 additional Simple action this \emph{beat} \\
\makeitem{Brace} & STR: 10 & 1 & 3+ & 1D & Remove 1+ damage tokens from \emph{Shield Up!}\newline This is a Simple action \\
\makeitem{Stance: Cat} & DEX: 10 & 1 & 3 & F & \emph{Reaction.} The character performs \emph{Get Up!} for free at the end of the \emph{counterbeat} \\
\makeitem{Dirty Trick} & INT: 9 & 1 & 4 & 3 & \emph{Reaction.} Inflict Blinded on the active enemy after it moves within 2 hexes \\
\makeitem{Dual Shot} & DEX: 12 & 1 & 4 & X & Commit the Draw \& Fire attack against two separate targets for Wep+1 \textbf{SP} cost. Subtract 1 from the max range.\newline This attack is affected by Take Aim \\
\makeitem{Fury} & STR: 12 & 2 & 5 & F & Any melee attack committed this \emph{beat} gains \emph{Unblockable} and \emph{Unparryable} \\
\makeitem{Juke} & DEX: 10 & 1 & 2 & X & \emph{Reaction.} Move 1.\newline Do not remove \emph{Shield Up!}\newline If ENC<=EQP/2 \emph{rd}, \textbf{SP} cost is 1D.\newline If ENC<=EQP, \textbf{SP} cost is 2.\newline IF ENC<=EQP*2, \textbf{SP} cost is 3.\newline IF ENC>EQP*2, \textbf{SP} cost is 4. \\
\makeitem{Stance: Leaf} & DEX: 8 & 1 & 3 & F & \emph{Reaction.} May move in any direction when suffering Knockback this \emph{counterbeat} \\
\makeitem{Leap} & DEX: 10\newline ENC<EQP & 1 & 2 & 2 & Move 2. Ignore any enemies, hazards, or half-cover obstacles while moving.\newline This is a Simple action\\
\makeitem{Persevere} & END: 12 & 1 & 5 & F & Gain 1 Enhanced Defense: \textbf{P.DEF} (1) token \\
\makeitem{Slink} & DEX: 12 & 4 & 3 & Wep*2 & Functions the same as Backstab \\
\makeitem{Taunt} & INT: 8 & 1 & 3 & 1D & 1 \emph{Intelligent} enemy within 5 hexes removes \emph{Shield Up!} and makes an immediate Move towards the character \\
\makeitem{Warcry} & - & 1 & 3 & F & Re-roll a single \textbf{SP} Die. Remember that re-rolls are always once-per-die and the second result is final\\
\hline
\end{tabularx}
\end{center}