\subsection{Revelations}
The worship of Av*rn-Z*l is already an occult religion, yet it still manages to retain its own sect of gnostics--a secretive cult within a secretive cult. These gnostics contemplate the Mystic Keys in search of Revelations: alternative meanings behind its words and parables. These profane meanings pervert the power of the Keys, producing verso-miracles. Revelations are also thought, not spoken; and this suspicious silence only lends to their dark reputation. The practice of Revelations has long been branded as blasphemy by the Inner Circle, and has led to burnings and even internally-led pogroms.

\begin{itemize}
\item \textbf{Catalyst:} Icons (Optionally)
\item \textbf{Bonus:} \textbf{DB}
\item \textbf{Notes:} Each Revelations attunement is derived from an identical entry in the Mystic Keys roster. Attuning an entry from the Keys also gives the character access to its twin in the Revelations roster. The character must still meet any requirements for the version they wish to activate. In-game, the character will only encounter these attunements via their entry in the Mystic Keys roster
\end{itemize}

\begin{tcolorbox}
\textbf{Note:} The status sheet is limited to 1 Mantra token, regardless of the mantra’s version.
\end{tcolorbox}

\begin{center}
\begin{tabularx}{\textwidth}{p{0.1\textwidth}p{0.1\textwidth}p{0.05\textwidth}p{0.05\textwidth}p{0.1\textwidth}p{0.46\textwidth}}
\hline
\rowcolor{white} \textbf{Name} & \textbf{Req} & \textbf{Int} & \textbf{FP} & \textbf{SP} & \textbf{Effects}\setcounter{rownum}{0}\\
\hline
Mantra: Dedication & INT: 8\newline FTH: 10 & - & 2 & F & Immediately after rolling the \emph{stamina pool}, the character may spend a single \textbf{SP} die to restore \textbf{FP} equal to that die’s score\\
Hope & INT: 10\newline FTH: 8 & - & 4 & 2 & Inflict Blinded on any visible enemy \\
Masin Crosses the River & INT: 8\newline FTH: 8 & - & 2 & 3 & Deal \textbf{PWR} Dark ranged damage to any visible enemy \\
Praise & INT: 8\newline FTH: 10 & - & 2+ & 3 & Deal \textbf{PWR}+ \emph{Unblockable} and \emph{Undodgeable} Dark ranged damage to an enemy within 5 hexes \\
Smite & INT: 12\newline FTH: 12 & - & 6 & 4 & Fill all the Defense \emph{sinks} of any visible enemy \\
Succor & INT: 10\newline FTH: 8 & - & 3 & 2D & Inflict Bleeding on any visible enemy \\
\hline
\end{tabularx}
\end{center}