This underground dock is built within a natural cavern that opens onto a river. The builders of this prison likely picked its location based on this feature. A single pier extends halfway to the mouth of the cave, and decaying floorboards serve as a rudimentary boardwalk. This boardwalk isn’t fixed to the cavern floor at all. Its boards were just left on the ground--understandably so, considering the task of pounding nails into bedrock.\\

Two rows of stone pillars line the way to the pier. These are not natural features, instead consisting of shallow cylinders stacked atop each other. Their stone is a much lighter shade than the rest of the cavern; they were likely imported from somewhere else.\\

The broken bodies of two dozen guards are strewn about the area. Some were gored, others were flattened, and still some were smashed against the pillars, leaving red smears across their white stone. The carnage looks to be days old. The Auroks too, lays amongst its victims.\\

A single dinghy is tied to the pier, bobbing gently against its mooring. Goldhand Jacquelyn waits aboard. At the foot of the pier, a few cargo boxes and burlap sacks have been left staged. Presumably, these would have been carried off into the prison complex had that Auroks not arrived.\\

> Speak with the mercenary -- \turnto{c43}\\
> Ascend to the rotunda -- \turnto{c31}\\
> Scavenge through the guards’ remains -- \turnto{c44}\\
> Examine the staged cargo -- \turnto{c45}\\
> Take a well-deserved \emph{short reprieve}\\
> Access your stash\\
\requiresx{c43a} Voyage onward -- \turnto{c42}