One by one, the Everloyal pile into the dinghy and find their seats along its gunwale. A section of its frame is missing--ripped away, or perhaps bitten off. Littletongue, the last to board, is the odd-girl-out. She casts about the vessel listlessly for a few moments before settling down on the center thwart.\\

“All settled then?”\\

Niki clambers up the bowsprit and hangs a lantern from it. It’s a decent effort but the gentle, yellow glow stands a poor chance against the all-encompassing Malediction.\\

“Well?”\\

“Aye. Get on with it, hireling. To Gran Selidore.”\\

Jacquelyn presses her foot against the pier and gives it a strong shove. The dinghy rocks to and fro, prompting everyone to latch onto various handholds. But it soon settles out, and Jacquelyn grabs the rudder from its sculling notch.\\

And so... a vagabond; zealot of the Inner Circle; unscrupulous mercenary; two academics; talking rat; and, of course, their champion pass through the cave mouth and into the opaque, gray abyss of the outside world. The entirety of the rag-dressed crusade for the resurrection of a dead god--\emph{second attempt}--is borne upon a rickety dinghy helmed by a woman with no loyalties beyond coin.\\

Jacquelyn steers the little vessel downriver, and begins to hum idly to herself. Snippets of a foreign tongue slip sporadically into the song. Her knuckles tap out a rhythm on the rudder’s yard as you pass into the fog, and lose sight of the world.\\

This sense of blindness is unnerving at first. But, like most things, you grow used to it in time.\\

Your eyes close; and then they close again for a bit longer. And you can still hear that humming as your mind passes into the world of dreams: a well-deserved respite from what you’ve survived, and what’s yet to come.\\

>> \textbf{End Chapter}