A squeal of metal hinges startles you awake. He is back.\\

Once, this sound heralded a tray of watery and tasteless gruel, but lately its meaning has twisted in an ironic perversion. The orange glow of his torch strengthens as he makes his way up the hall. Is it you today? No, he stops at a neighboring cell. The comrade within had ceased moaning two, three--maybe even four days prior.\\

The torch flame wavers as he fiddles with the lock. In his other hand, a meat hook is swept by a wicked sheen. He fishes through the cell with it, then pulls out a corpse by its leg. You duck when he turns--a hair too late. The jailer pauses in his grisly labor, mumbles something to himself, laughs, and then growls.\\

His face appears in the slit window of your cell. Fully hollowed. A pair of dark eyes stare into your own for a moment, and then you hear the jangling of keys...\\

>> Equip the Prisoner Chains set (\hyperlink{Prisoner Chains}{Page \pageref*{Prisoner Chains}}) on the character sheet. You may not unequip this outfit at this time.\\
\requires{8+ INT} You were prepared for this eventuality. Add the weapon Loose Cobblestone (\hyperlink{Loose Cobblestone}{Page \pageref*{Loose Cobblestone}}) to the character sheet.\\
\requires{10+ INT} You prepared well indeed. Add the weapon Sock Full of Rocks (\hyperlink{Sock Full of Rocks}{Page \pageref*{Sock Full of Rocks}}) to the character sheet instead of a Loose Cobblestone.\\
>> Otherwise, you will be using your fists (\hyperlink{Fist}{Page \pageref*{Fist}}).\\

>> Fight for your life -- \turnto{c12}