It’s only a short trip down the stairwell before you run into your ratfriend again. Niki stands facing a strange sight indeed: a sheet of solid fog. It fills the archway of the landing with unnerving perfection, as if some mad mason had run out of stones and so repurposed the air itself to complete his work.\\

You approach the fog wall, arm outstretched, and its wispy tendrils seem to react to your presence... reaching out to you in kind. Ratfriend Niki gives a shout, and you pull your arm back.\\

“No-no. Bad. No.”\\
It shakes its head rapidly, as if chasing rain from its fur.\\

“Come-come.”\\
Ratfriend Niki beckons you over to the next flight of stairs--or what was once stairs. Its soffit has suffered a total collapse, obstructing the landing below. Niki manages to squirm its way down through the rubble, and peers up at you from the other side. It doesn’t take much measuring to see that you won’t be capable of following. Despite its animal appearance, the guilt on Ratfriend Niki’s face is apparent.\\

“Thank-yoo, O-friend. Very trust.”\\

“Take sippy?”\\
It rifles through its rags, and produces something surprising: a sunlit flask. Quite the treasure to smuggle into such a place--this “sippy”--let alone keep it hidden from the guards. Niki heaves the flask up through the rubble with a two-handed lob, landing it in your hands.\\
\gain{Sunlit Flask}\\

“Sippy.”\\
It mimics a drinking motion, rubbing its furred belly.\\

“Come-come. Down.”\\
And with that, Ratfriend Niki is gone.\\

Behind you, the fog wall billows in menacing invitation--as if it were taunting you with your lone means of progress. Whatever it was that scared Ratfriend Niki off, you’ll have to face the threat down by yourself if you’re to escape from this place.\\

>> Cross the fog-choked archway -- \turnto{c19}